Age-related changes in plant growth and traits

### 2016-02-04 Accessory_figs_2016.Rmd
work on accessory costs

#Figure 1. Correlations of various reproductive investment categories against plant weight
```{r}
win.metafile("figs2/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
plot

@@

#Appendix Fig 1. Correlations with leaf investment  
* if you change conditions to "growth_leaf>50" to remove those old individuals that are no longer replacing leaves, the correlations become ~2x as strong
```{r}
win.metafile("figs2/Appendix01_correlations_with_leaf_investment.wmf", height=9, width=9)
plot

@@

write.csv(acc_costs_spp, file="figs2/Table01_AccCosts_by_Species.csv",row.names=FALSE)
```

#Figure 2 and Table 2. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Figure02_acc_cost_seed_size_4panel.wmf", height=9, width=9)
plot

@@

Table2 <- data.frame(component=c("total accessory costs","b div p","c div p","dispersal"))
Table2$intercept = c(slopes2[1],slopes3[1],slopes4[1],slopes5[1])
Table2$slope = c(slopes2[2],slopes3[2],slopes4[2],slopes5[2])
write.csv(Table2, file="figs2/Table02_AccCosts_coeff.csv",row.names=FALSE)

@@

#Table 3 and Figure 3.Per seed accessory costs are lower in individuals with higher seed count. 
###This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
```{r}
win.metafile("figs2/Figure_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
plot

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table03_seedcount_vs_accessory.csv",row.names=FALSE)

@@

#Table 3 extra - showing propagule investment instead of seed_count. Could also replace with seedset
```{r}
win.metafile("figs2/Figure_EXTRA_acc_cost_by_seedset.wmf", height=5, width=5)
plot

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table03a_seedset_vs_accessory.csv",row.names=FALSE)

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table04_accessory_vs_RE.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table05_accessory_vs_RA.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table04c_accessory_vs_total_weight.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table04d_accessory_vs_age.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table06b_total_size_by_seedset.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table08a_b_div_p_vs_seedset.csv",row.names=FALSE)
```

@@

results$species <- c("Boronia ledifolia","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table08b_c_div_p_vs_seedset.csv",row.names=FALSE)
```

@@

data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0&species!="LEES")
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

plot(packaging_dispersal_per_seed~seedset,data=subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0&species!="LEES"),col=col.spp(species),pch=16,log="xy")

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table08c_dispersal_vs_seedset.csv",row.names=FALSE)
```

#need to redo this, deleted code that created dataframe
```{r}
win.metafile("figs2/dispcosts_vs_ovules.wmf", height=6, width=6)
plot
par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
plot(ovules~r.squared,results,log="y",col=col.spp(species),pch=16,cex=2,las=.1)
mod <- lm(r.squared~log10(ovules),results)
words.bottom.right.logy(mod)
dev.off()
```

@@

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="GRBU"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="GRSP"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="HATE"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="HEPU"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,age>2&b_div_p>0&c_div_p>0&species=="LEES"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PELA"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PEPU"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PHPH"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PILI"))
summary(mod)

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PUTU"))
summary(mod)
```
#*******************************
#below this line: results probably not used in manuscript
#*******************************
#With increasing seed count, not only do total per seed accessory costs decline, but so do the individual components. 
```{r}
xvar <- "seed_count"
yvar <- "b_div_p"

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table07a_b_div_p_vs_seed_count.csv",row.names=FALSE)
```

@@

results$species <- c("Boronia ledifolia","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table07b_c_div_p_vs_seed_count.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Table07c_dispersal_vs_seed_count.csv",row.names=FALSE)
```

>>>>

#Figure 1. Correlations of various reproductive investment categories against plant weight
```{r}
win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
plot

@@

#In other words, for many species, seed counts do not provide an accurate estimate of reproductive investment
```{r}
data <- subset(SummaryInd,seed_count>0)
data <- split(data, data$species)

xvar <- "repro_inv"
yvar <- "seed_count"

lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))

data <- subset(SummaryInd,seed_count>0)
data <- split(data, data$species)

results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
write.csv(results, file="figs2/Accessory_Costs/Table01a_seed_count_vs_repro_inv.csv",row.names=FALSE)
```

```{r}
data <- subset(SummaryInd,seed_count>0)
data <- split(data, data$species)

xvar <- "repro_inv"
yvar <- "diameter"

lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))

data <- subset(SummaryInd,seed_count>0)
data <- split(data, data$species)

results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
write.csv(results, file="figs2/Accessory_Costs/Table01b_diameter_vs_repro_inv.csv",row.names=FALSE)
```

```{r}
data <- subset(SummaryInd,seed_count>0)
data <- split(data, data$species)

xvar <- "repro_inv"
yvar <- "repro_all_count"

lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))

data <- subset(SummaryInd,seed_count>0)
data <- split(data, data$species)

results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
write.csv(results, file="figs2/Accessory_Costs/Table01c_repro_all_count_vs_repro_inv.csv",row.names=FALSE)
```

#Appendix Fig 1. Correlations with leaf investment  
* if you change conditions to "growth_leaf>50" to remove those old individuals that are no longer replacing leaves, the correlations become ~2x as strong
```{r}
win.metafile("figs2/Accessory_Costs/Appendix01_correlations_with_leaf_investment.wmf", height=9, width=9)
plot

@@

write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table02_AccCosts_by_Species.csv",row.names=FALSE)
```

#Figure 2 and Table 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure02_acc_cost_seed_size_4panel.wmf", height=9, width=9)
plot

@@

Table3 <- data.frame(component=c("total accessory costs","b div p","c div p","dispersal"))
Table3$intercept = c(slopes2[1],slopes3[1],slopes4[1],slopes5[1])
Table3$slope = c(slopes2[2],slopes3[2],slopes4[2],slopes5[2])
write.csv(Table3, file="figs2/Accessory_Costs/Table03_AccCosts_coeff.csv",row.names=FALSE)

@@

#Table 4 and Figure 3.Per seed accessory costs are lower in individuals with higher seed count. 
###This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
```{r}
win.metafile("figs2/Accessory_Costs/Figure_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
plot

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table04a_seedcount_vs_accessory.csv",row.names=FALSE)

@@

#Table 4 extra - showing propagule investment instead of seed_count. Could also replace with seedset
```{r}
win.metafile("figs2/Accessory_Costs/Figure_EXTRA_acc_cost_by_seedset.wmf", height=5, width=5)
plot

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table04b_seedset_vs_accessory.csv",row.names=FALSE)

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_RA.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_total_weight.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table05d_accessory_vs_age.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table0xx_total_size_by_seedset.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table06a_b_div_p_vs_seedset.csv",row.names=FALSE)
```

@@

results$species <- c("Boronia ledifolia","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table06b_c_div_p_vs_seedset.csv",row.names=FALSE)
```

@@

data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

plot(packaging_dispersal_per_seed~seedset,data=subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0),col=col.spp(species),pch=16,log="xy")

@@

results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,40,2,20,2)
max_seedset <- select(SummarySpp[["max"]],species,seedset) 
min_seedset <- select(SummarySpp[["min"]],species,seedset) 
results <- merge(results, max_seedset, by=c("species"), all=TRUE)
results <- merge(results, min_seedset, by=c("species"), all=TRUE)
names(results)=c("species","r2","p-value","n","intercept","slope","ovules_per_fruit","max_seedset","min_seedset")

#results$min_pack <- (10^results$intercept) + (results$slope*results$max_seedset)
#results$max_pack <- (10^results$intercept) + (results$slope*results$min_seedset)
results

win.metafile("figs2/Accessory_Costs/Table07_dispcosts_vs_ovules.wmf", height=6, width=6)
plot

par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
plot(ovules_per_fruit~r2,data=subset(results,species!="PELA"),log="y",col=col.spp(species),pch=16,cex=2)
mod <- lm(r2~log10(ovules_per_fruit),data=subset(results,species!="PELA"))
words.bottom.right.logy(mod)
dev.off()

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")

results

write.csv(results, file="figs2/Accessory_Costs/Table06c_dispersal_vs_seedset.csv",row.names=FALSE)
```

@@

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="GRBU"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("GRBU")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="GRSP"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("GRSP")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="HATE"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("HATE")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="HEPU"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("HEPU")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,age>2&b_div_p>0&c_div_p>0&species=="LEES"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("LEES")
species_effects2$effects <- c("intercept","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PELA"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("PELA")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PEPU"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("PEPU")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PHPH"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("PHPH")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PILI"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("PILI")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PUTU"))
summary(mod)
species_effects2 <- as.data.frame(coef(mod))
names(species_effects2) = c("PUTU")
species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")

write.csv(species_effects, file="figs2/Accessory_Costs/Table08_breaking_down_accessory_costs_spp.csv",row.names=FALSE)
```

#looking at how the slopes of the relationship between accessory investment and propagule investment shift across species 
##slopes only statistically different from 1 in 2 species
##intercepts quite variable - means that the "baseline" accessory investment, before you get any propagules varies
```{r}
par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1)) 
plot(propagule_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0&propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlab="total accessory investment (mg)",ylab="total propagule investment (mg)")
slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data=subset(SummaryInd,propagule_inv>0))
summary(slope_check)

data <- select(SummaryInd,species,propagule_inv,accessory_inv)
data <- subset(data,propagule_inv>0)
data <- split(data, data$species)

for(i in 1:14) {
slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data[[i]],slope.test=1)
summary(slope_check)
}

xvar <- "accessory_inv"
yvar <- "propagule_inv"

lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))

data <- subset(SummaryInd,propagule_inv>0)
data <- split(data, data$species)

results <- summarise_all_fits(lmfits)

for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
```

species with bigger seeds, lower seedset spend less per flower. Here taking the percent of the cost to make a single flower that goes into pre-pollination parts

```{r}
par(mfrow=c(2,2), cex=1, omi=c(1,0.1,.1,0.05), mai=c(.2,.55,.1,0.1))

plot(percent_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
mod <- lm(log10(seed_size)~log10(percent_prepollencosts),data=subset(SummarySpp[["mean"]]))
words.bottom.left.logxy(mod)

plot(percent_prepollencosts~seedset,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
mod <- lm(log10(seedset)~log10(percent_prepollencosts),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)

plot(percent_dispersalcosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
mod <- lm(log10(seed_size)~log10(percent_dispersalcosts),data=subset(SummarySpp[["mean"]]))
words.bottom.left.logxy(mod)

plot(percent_dispersalcosts~seedset,data=subset(SummarySpp[["mean"]],percent_dispersalcosts>0),col=col.spp(species),pch=16,log="xy",cex=1.5)
mod <- lm(log10(seedset)~log10(percent_dispersalcosts),data=subset(SummarySpp[["mean"]],percent_dispersalcosts>0))
words.top.left.logxy(mod)
```

SummarySpp[["mean"]]$percent_dispersalcosts
#*******************************
#below this line: results probably not used in manuscript
#*******************************
#With increasing seed count, not only do total per seed accessory costs decline, but so do the individual components. 
```{r}
xvar <- "seed_count"
yvar <- "b_div_p"

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table0xx_b_div_p_vs_seed_count.csv",row.names=FALSE)
```

@@

results$species <- c("Boronia ledifolia","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table0xx_c_div_p_vs_seed_count.csv",row.names=FALSE)
```

@@

results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata") 
names(results)=c("species","r2","p-value","n","intercept","slope")
results
write.csv(results, file="figs2/Accessory_Costs/Table0xx_dispersal_vs_seed_count.csv",row.names=FALSE)
```

plot(propagule_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,1000000),ylim=c(1,50000),xaxt="n")
mod <- lm(log10(repro_inv)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)
#mtext(text="investment in propagules (mg)",side=2,line=2.3,outer=FALSE)
